---
title: 'Leaflet Assignment: Tech Giants'' Offices in London'
author: "Gary Mu"
always_allow_html: yes
output:
  html_document:
    code_folding: hide
---

## Introduction

This is an assignment for Data Products, which is one of the courses 
under Coursera Data Science cluster.

In this assignment, I am going to utilize Leaflet mapping functionality to create 
an interactive map that will pinpoint the giant tech offices (Google, King, Facebook, etc)
in London. Note that the office locations are from public information sources like 
Google maps with no proprietary information. 

## Load the necessary packages
```{r, echo=FALSE, message=FALSE}
require(leaflet)
require(tidyverse)
```


## Create map object and showcase London

Now I will create a map object from leaflet, and pinpoint London city from tile 
to show London city from the map tile. 

```{r}
london <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lat = 51.52, lng = -0.11, popup = 'London City')
  
london
```

## Adding tech company markers

Now I will add markers of the tech companies' offices.
I will add office locations of the following companies: 
Google, Facebook, King, Twitter, Microsoft, Linkedin and Youtube.

You can click on the icons to view more details of the office addresses, or
link to the company's "about me" pages.

#### December 4th, 2017

```{r}

companies <- c('Twitter', 'Google-cental', 'Google-kingscross' , 'Youtube',
               'Facebook-brock', 'Facebook-rothbone', 'King', 'Microsoft', 'Linkedin')

company_latlon <- data.frame(
    lat = c(51.510579, 51.516047, 51.533598, 51.532831, 51.525697, 51.517099, 51.515457, 51.519460, 51.516202),
    lng = c(-0.136577, -0.127648, -0.126365, -0.125935 , -0.139754, -0.133619, -0.135509, -0.181427, -0.128148)
)

logos <- makeIcon(
    iconUrl = c(
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/twitter-128.png', #twitter
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/google_-128.png', #google
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/google_-128.png', #google
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/youtube-128.png', #Youtube
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/facebook-128.png', #facebook
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/facebook-128.png', #facebook
      'https://care.king.com/data/king_qna_en/media/members/image/68/93/53/179/3716/5619ea3416a50d3b/thumbs/king_50_50_DEFAULT_cropfit_NORTH.jpg', #king
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/microsoft-128.png', #microsoft
      'https://cdn1.iconfinder.com/data/icons/smallicons-logotypes/32/linkedin-128.png' #linkedin
      ),
    iconWidth = 31, iconHeight = 31,
    iconAnchorX = 31*215/230/2, iconAnchorY = 1
)


twitter_info <- paste(sep = "<br/>",
  "<b><a href='http://about.twitter.com'>About Twitter</a></b>",
  "20 Air St, Soho",
  "London W1B 5AG"
)

google_info_central <- paste(sep = "<br/>",
  "<b><a href='http://google.com/about'>About Google</a></b>",
  "1-13 St Giles High St",
  "London WC2H 8AG"
)

google_info_kings <- paste(sep = "<br/>",
  "<b><a href='http://google.com/about'>About Google</a></b>",
  "6 Pancras Square, Kings Cross",
  "London N1C 4AG"
)

youtube_info_kings <- paste(sep = "<br/>",
  "<b><a href='http://google.com/about'>About Youtube</a></b>",
  "6 Pancras Rd, Kings Cross",
  "London N1C 4AG"
)

facebook_info_central <- paste(sep = "<br/>",
  "<b><a href='http://facebook.com/about'>About Facebook</a></b>",
  "10 Brock St",
  "London NW1 3FG"
)

facebook_info_rothbone<- paste(sep = "<br/>",
  "<b><a href='http://facebook.com/about'>About Facebook</a></b>",
  "35 Rathbone Pl, Fitzrovia",
  "London W1T 1QU"
)

king_info <- paste(sep = "<br/>",
  "<b><a href='http://www.king.com/about'>About King</a></b>",
  "178 Wardour St, Soho",
  "London W1F 8FY"
)

linkedin_info <- paste(sep = "<br/>",
  "<b><a href='http://www.king.com/about'>About King</a></b>",
  "Castlewood House, 77-91 New Oxford St",
  "London WC1A 1DG"
)

microsoft_info <- paste(sep = "<br/>",
  "<b><a href='http://www.king.com/about'>About King</a></b>",
  "2 Kingdom St",
  "London W2 6BD"
)


company_latlon %>%
    leaflet() %>%
    addTiles() %>%
  addMarkers( icon = logos,
              popup = c(twitter_info,
                        google_info_central,
                        google_info_kings,
                        youtube_info_kings,
                        facebook_info_central,
                        facebook_info_rothbone,
                        king_info,
                        microsoft_info,
                        linkedin_info
              ))

```


